\enes{\section{Publications}}{\section{Publicaciones}}

\subsection{Undergraduate Project}

\cvitem{2014}{
  \emph{Category Theory Applied to Functional Programming}.
  Supervisor: Andrés Sicard Ramírez.
  Systems Engineering undergraduate project.
  Universidad EAFIT.
  Honorable mention.
}

\subsection{Blog posts and tutorials}

\cvitem{2016}{
  \href
  {https://www.stackbuilders.com/tutorials/haskell/csv-encoding-decoding/}
  {CSV encoding and decoding in Haskell with Cassava}
}

\cvitem{2015}{
  \href
  {https://www.stackbuilders.com/news/reverse-reverse-theorem-proving-with-idris}
  {Reverse, reverse: theorem proving with Idris}
}

\cvitem{}{
  \href
  {https://www.stackbuilders.com/news/a-quickcheck-tutorial-generators}
  {A QuickCheck tutorial: generators}
}

\cvitem{}{
  \href
  {https://www.stackbuilders.com/news/the-hang-of-elm-hangman-and-functional-programming-with-elm}
  {The hang of Elm: hangman and functional programming with Elm}
}

\cvitem{}{
  \href
  {https://www.stackbuilders.com/news/errors-and-exceptions-in-haskell}
  {Errors and exceptions in Haskell}
}

\cvitem{}{
  \href
  {https://www.stackbuilders.com/news/dr-hakyll-create-a-github-page-with-hakyll-and-circleci}
  {Dr. Hakyll: create a GitHub page with Hakyll and CircleCI}
}

\cvitem{}{
  \href
  {https://www.stackbuilders.com/news/obverse-versus-reverse-benchmarking-in-haskell-with-criterion}
  {Obverse versus reverse: benchmarking in Haskell with Criterion}
}

% \cvitem{}{
%   \href
%   {https://www.stackbuilders.com/news/how-to-program-it}
%   {How to program it}
% }

\cvitem{}{
  \href
  {https://www.stackbuilders.com/news/hangman-imperative-functional-programming}
  {Hangman: imperative functional programming}
}

\cvitem{}{
  \href
  {https://www.stackbuilders.com/news/pattern-matching-wot-s-uh-the-deal}
  {Pattern matching: Wot's... Uh the Deal?}
}

% \cvitem{}{
%   \href
%   {https://www.stackbuilders.com/news/the-notes-of-ghc}
%   {The notes of GHC}
% }

% \cvitem{}{
%   \href
%   {https://www.stackbuilders.com/news/obverse-and-reverse}
%   {Obverse versus reverse}
% }

\cvitem{2014}{
  \href
  {https://www.stackbuilders.com/news/the-weak-and-the-strong-functors}
  {The weak and the strong: functors}
}

\cvitem
{More}
{\link{https://www.stackbuilders.com/news/author/juan-pedro-villa}}

\subsection{Presentations}

% \cvitem{2013/09/25}{
%   \emph{Enoch: Just Enoch},
%   Logic and Computation Seminar,
%   Universidad EAFIT.
% }

% \cvitem{2013/04/19}{
%   \emph{Enoch: Not the father of Methuselah},
%   Logic and Computation Seminar,
%   Universidad EAFIT.
% }

% \cvitem{2013/03/22}{
%   \emph{Enoch: The father of Irad},
%   Logic and Computation Seminar,
%   Universidad EAFIT.
% }

% \cvitem{2013/02/22}{
%   \emph{Enoch: A son of Cain},
%   Logic and Computation Seminar,
%   Universidad EAFIT.
% }

\cvitem{2009}{
  \emph{Proofs $=$ Programs: Functional programming with dependent types},
  Días de la Ciencia Aplicada 2009,
  Universidad EAFIT.
}

\cvitem{}{
  \emph{Non-dependent Types for the Implementation of a Dependently
    Typed Functional Programming Language},
  Logic and Computation Seminar,
  Universidad EAFIT.
}

\cvitem{2007}{
  \emph{Regular Expressions Using Haskell},
  Logic and Computation Seminar,
  Universidad EAFIT.
}
